Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-12-31 Ben_Manuscripts/stochastic_transport/Draft.tex
New charts explaining beta parameter

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model and the MSDDM in order to demonstrate how one can use their realizations
  in order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
  similar to the 1-mode sFLMcut model at a lower computational cost and is far more
  accurate than sFBM and sFLM. The 2-mode model has a broken correlation structure, so 
  we do not consider it here.

  %MRS5: One question is if other method would lead to substantially
  %different results for fluxes or selectivity.  May need too think
  %about justification more if just one method is mentioned.
  %BJC5: Added MSDDM

  %MRS5: I think it might be useful to have at least visualizions of
  %distribution of FPT and its fit. It might not be obvious to
  %readers that the different mechanisms have distributions of FPT
  %that are well decscribed by the relatively simple moving diffusion
  %equation in eq 15. 
  %BJC5: added to figure

@@

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
  and used the expected value of the analytical equation to calculate flux from 
  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves}, 
  the flux appears to scale according to a power law of the form:
  \begin{equation}
  J(L) = cL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}
  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.

  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
  %BJC: should have a paragraph about c -- roughly follows their MSDs.
  \begin{figure}
  \centering
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_regular}
  \end{subfigure}
  % BJC: could use better color scheme. Maybe outline hurst parameters
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{c_parameters.pdf}
  \caption{}\label{fig:c_parameters}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{beta_parameters.pdf}
  \caption{}\label{fig:beta_parameters}
  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
%  \caption{}\label{fig:mfpt_curves}
%  \end{subfigure}
  %BJC: going out to 3 decimal places seems silly
  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curves_brownian}
%  \end{subfigure}
  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
  % have each just show 1 point? 
  \caption{(a) The single particle solute flux decays with increasing pore length. 
  Solutes with high MSDs have higher fluxes. (b) We fit the single particle solute flux 
  versus pore length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed 
  lines in (a)). Solutes with higher fluxes have higher values of $c$. Solutes with 
  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
  correlation between hops (set $H$=0.5), the flux increases significantly and 
  $\beta \sim 2$ for all solutes independent of dwell distribution
  parameters.}\label{fig:flux_curves}
  \end{figure}

  %MRS5: Does't fitting to eq 15 cut down on the expense of the number of trajectories
  %by a fair amount?  Should there be some discussion of this? 
  %BJC5: added this
  It is only necessary to simulate 1000 realizations of each model in order to
  parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory realizations 
  in order to generate Figure~\ref{fig:flux_curves}, however, in Figure~\ref{S-fig:flux_curve_sensitivity}
  of the Supporting information, we show that one can still show statistically
  significant differences in solute flux with as little as 100 trajectory 
  realizations. To be sure, we recommend simulating at least 1000 realizations. 
  Since the computational cost of the MSDDM is greater than the AD model, we 
  generated flux curves using only 1000 realizations at each pore length.

  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux?
  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
  solute MSD while the value of the growth exponent, $\beta$, is inversely 
  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
  were uncorrelated. Regardless of the parameters of the dwell time distribution,
  the growth exponent is always about 2, the same value that we observe for 
  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
  Supporting Information).

  %MRS5: probably the figure showing beta \sim 2 can be in supporting
  %information, and you just state the result here.

  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
  highlights that anti-correlation between hops plays a major role in solute flux.
  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
  difference will only grow with increasing pore length. Note also that the ranking
  of solute fluxes changes. Methanol jumps from the second lowest to the highest
  flux when we remove hop correlation. The high degree of anti-correlation among
  hops made by methanol outweighs its relatively wide hop length distribution.

>>>>

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model and the MSDDM in order to demonstrate how one can use their realizations
  in order to calculate the flux (see section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
  similar to the 1-mode sFLMcut model at a lower computational cost and is far more
  accurate than sFBM and sFLM. The 2-mode AD model has a broken correlation structure, 
  so we do not consider it here.

@@

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
  and used the expected value of the analytical equation to calculate flux from 
  Equation~\ref{eqn:hill_relation}. As shown in Figures~\ref{fig:flux_curves_ad} and
  \ref{fig:flux_curves_msddm}, the flux appears to scale according to a power law 
  of the form:
  \begin{equation}
  J(L) = cL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}
  %while the MFPT scales as its inverse, $(1/c)L^{\beta}$.

  %BJC: need simulations with increased length for L=35-50 nm pores of acetic acid and methanol
  %BJC: see of clauset has better way of fitting t^-alpha (alpha might be too big)
  %BJC: should have a paragraph about c -- roughly follows their MSDs.
  \begin{figure}
  \centering
  %BJC5: TODO: make same figure for msddm
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{sFBMcut}\label{fig:flux_curves_ad}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_msddm.pdf}
  \caption{MSDDM}\label{fig:flux_curves_msddm}
  \end{subfigure}  
  \caption{(a) The distributions of passage times generated from the sFBMcut model
  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
  solutes as well as the MSDDM in Figures~\ref{S-fig:ad_fpt_fits} and~\ref{S-fig:msddm_fpt_fits}
  of the Supporting Information. (b) The single particle flux measured 
  by the sFBMcut AD model and (c) the MSDDM decays with increasing pore length. 
  The rankings of solute fluxes are consistent with the MSDs predicted by each model.
  The ranking of the MSDDM is most consistent with MD MSDs. The MSDDM predicts higher
  fluxes than the sFBMcut model. We fit the single particle solute flux versus pore
  length, $L$, to a power law function of the form $cL^{-\beta}$ (dashed lines in (b)
  and (c)). 
%  Solutes with higher fluxes have higher values of $c$. Solutes with 
%  smaller Hurst parameters, $H$, have larger values of $\beta$. (c) If we remove 
%  correlation between hops (set $H$=0.5), the flux increases significantly and 
%  $\beta \sim 2$ for all solutes independent of dwell distribution
%  parameters.
  }\label{fig:flux_curves}
  \end{figure}

  % BJC: could use better color scheme. Maybe outline hurst parameters
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{c_parameters.pdf}
%  \caption{}\label{fig:c_parameters}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
%  \caption{}\label{fig:beta_parameters}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
%  \caption{}\label{fig:mfpt_curves}
%  \end{subfigure}
  %BJC: going out to 3 decimal places seems silly
  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curves_brownian}
%  \end{subfigure}
  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
  % have each just show 1 point?

  We determined that it is only necessary to simulate 1000 realizations of each model
  in order to parameterize Equation~\ref{eqn:flux_decay}. We used 10000 trajectory
  realizations in order to generate each point in Figure~\ref{fig:flux_curves_ad}, 
  however, in Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting information,
  we show that one can still show statistically significant differences in solute 
  flux, with minimal change to the mean flux values, using as few as 100 trajectory
  realizations. To be sure, we recommend simulating at least 1000 realizations. 
  Since the computational cost of the MSDDM is greater than the AD model, we generated
  each point of the flux curves in Figure~\ref{fig:flux_curves_msddm} using only 1000
  realizations at each pore length.

  Anti-correlation between solute hops has a significant effect on the scaling
  of solute flux with pore length. In Figure~\ref{fig:beta_hurst}, we show that 
  $\beta$, as derived from the sFBMcut model, is inversely related to the Hurst
  parameter while $\beta$, as derived from the MSDDM, shows no discernible
  trend.

  \begin{figure}
  \centering
  \begin{subfigure}{0.43\textwidth}
  \includegraphics[width=\textwidth]{beta_hurst.pdf}
  \caption{}\label{fig:beta_hurst}
  \end{subfigure}
  \begin{subfigure}{0.52\textwidth}
  \includegraphics[width=\textwidth]{beta_parameters.pdf}
  \caption{}\label{fig:beta_parameters}
  \end{subfigure}
  \end{figure}

%  \begin{figure}
%  \centering
%  % bar charts
%%  \begin{subfigure}{0.45\textwidth}
%%  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
%%  \end{subfigure}
%%  \begin{subfigure}{0.45\textwidth}
%%  \includegraphics[width=\textwidth]{beta_parameter_comparison.pdf}
%%  \end{subfigure}
%  \includegraphics[width=0.5\textwidth]{beta_c_parameter_comparison.pdf}
%  \caption{}\label{fig:flux_parameters}
%  \end{figure}

  %MRS5: probably the figure showing beta \sim 2 can be in supporting
  %information, and you just state the result here.
  %MRS: can you put a physical thesis here, not just a mathematical one?  Why is this change in parameters important to flux? 
%  The prefactor, $c$, in Equation~\ref{eqn:flux_decay} grows with increasing
%  solute MSD while the value of the growth exponent, $\beta$, is inversely 
%  related to the Hurst parameter, $H$ (see Figure~\ref{fig:flux_parameters}).
%  In Figure~\ref{fig:flux_curves_brownian}, we removed the correlation 
%  structure (set $H$=0.5) from AD trajectory realizations so that all hops 
%  were uncorrelated. Regardless of the parameters of the dwell time distribution,
%  the growth exponent is always about 2, the same value that we observe for 
%  Brownian motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the 
%  Supporting Information).

% BJC: following is wrong
%  Dwell times between hops have a significant effect on the length dependence
%  of solute flux. The values of $\beta$ fit to realizations of the sFBMcut AD
%  model are significantly higher than the MSDDM. As evident by comparison of 
%  Figures~\ref{fig:msddm_eyetest} and~\ref{fig:ad_eyetest}, realizations of the
%  AD model exhibit much longer and more frequent periods of immobility. If we
%  generate realizations of the sFBMcut model without trapping (dwell times are
%  all 1 time step), the value of $\beta$ drops to 2 in all cases. In fact, we
%  observe the same value of $\beta$ for Brownian motion (see Figure blah of the 
%  Supporting Information) which implies that the Hurst parameter has no effect
%  on the length dependence of flux.
%  
%  Comparison of Figures~\ref{fig:flux_curves_regular} and~\ref{fig:flux_curves_brownian}
%  highlights that anti-correlation between hops plays a major role in solute flux.
%  With a pore length of 50 nm, the flux of the fasted moving solute, ethylene glycol is 
%  c.a. 5 times lower with versus without anti-correlated hops. The flux of the slowest
%  moving solute, acetic acid, is about 16 times lower by the same comparison. This 
%  difference will only grow with increasing pore length. Note also that the ranking
%  of solute fluxes changes. Methanol jumps from the second lowest to the highest
%  flux when we remove hop correlation. The high degree of anti-correlation among
%  hops made by methanol outweighs its relatively wide hop length distribution.

### 2019-12-31 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
New charts explaining beta parameter

%  We validated our approach to simulating trajectory realizations by testing
%  it against analytical solutions to the mean first passage time of a Brownian
%  particle with 2 absorbing boundaries.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
  \end{figure}

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curve_brownian}
  \end{figure}
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}

>>>>

%  We validated our approach to simulating trajectory realizations by testing
%  it against analytical solutions to the mean first passage time of a Brownian
%  particle with 2 absorbing boundaries.
  \subsection*{Analytical fits to MFPT distributions}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ad_fpt_distributions_URE.pdf}
  \caption{Urea}\label{fig:URE_ad_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ad_fpt_distributions_ACH.pdf}
  \caption{Acetic Acid}\label{fig:ACH_ad_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ad_fpt_distributions_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_ad_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ad_fpt_distributions_MET.pdf}
  \caption{Methanol}\label{fig:MET_ad_fpt_distributions}
  \end{subfigure}
  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
  first passage time distributions generated by 10,000 realizations of the 
  anomalous diffusion model. }\label{fig:ad_fpt_fits}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_URE.pdf}
  \caption{Urea}\label{fig:URE_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_ACH.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm_fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msddm_fpt_distributions_MET.pdf}
  \caption{Methanol}\label{fig:MET_msddm_fpt_distributions}
  \end{subfigure}
  \caption{We fit Equation~\ref{M-eqn:passage_times} of the main text to the
  first passage time distributions generated by 1000 realizations of the 
  Markov state dependent dynamical model. Note that we generated 10 times less
  realizations of the MSDDM which leads to noisier histograms. We show that
  this has a negligible effect on the fits in Figure~\ref{fig:flux_curve_sensitivity}.}\label{fig:msddm_fpt_fits}
  \end{figure}

%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{figure}
%  
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curve_brownian}
%  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}
